---
title: "GutMicro Workshop - Data wrangling challenges"
date: 'r Sys.Date()'
output:
  rmdformats::readthedown:
    toc_depth: 4
    collapsed: false
    code_folding: hide
    number_sections: true
    highlight: kate
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = TRUE)
library(tidyverse)
library(phyloseq)

```

# INTRO

This document contains a series of challenges that can be solved using functions from the tidyverse packages (mainly from dplyr and tidyr), but might not be limited to the functions included in the workshop.
The aim is to solve each challenge using these functions and with code that is easy to read and understand.

When finished knit the document and send the Rmarkdown file to me together with the output.

## load data

The challenges uses that data from the GlobalPatterns dataset

```{r}
data("GlobalPatterns")
GP.melt <- psmelt(GlobalPatterns)
```

# CHALLENGE 1

For each sampletype, what is the average number of unique genera per sample?

```{r challenge_1}

```

# CHALLENGE 2

Which bacterial family is most often the most abundant in the samples?

```{r challenge_2}

```

# CHALLENGE 3

What is the two most dominant genera per SampleType and what are their relative abundance?

```{r challenge_3}

```
